Covariate analysis of CMC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (ACC and DLPFC with CQN normlaisation)

### 2017-07-29 code/Rmd/CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_PENN.Rmd
Added markdown to process penn samples alone

knit2synapse::knitToFolderEntity(file = "./CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_MSSM.Rmd",
                                 parentId = "syn7501880",
                                 entityName = 'ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN - MSSM')
```

@@

METADATA = rbindlist(list(METADATA_ACC, METADATA_DLPFC), use.names = T, fill = T) %>%
  droplevels() %>%
  list(.,METADATA_QC) %>%
  join_all %>%
  dplyr::mutate(LibraryBatch = as.factor(LibraryBatch)) %>%
  left_join(ANCESTRY) %>%
  dplyr::filter(Institution == 'MSSM') %>%
  unique

@@

### Covariates clustering
Determine relationship between covariates. 
```{r covariates.clustering}
FactorCovariates <- c("Individual_ID", "Gender", "LibraryBatch", "Dx.Tissue", "RibozeroBatch", "FlowcellBatch")
ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate",
                    "GenesDetected", "TranscriptsDetected", "ExpProfEfficiency", "rRNARate", "TotalReads", 
                    "PercentAligned", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")

@@

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates
```{r preAdjusted.covariates, cache=TRUE}
# Find correlation between PC's of gene expression with covariates
preAdjustedSigCovars = runPCAandPlotCorrelations(CQN.GENE_EXPRESSION$E, 
                                                 COVARIATES,
                                                 'NULL design(voom-normalized)', 
                                                 isKeyPlot=TRUE, 
                                                 MIN_PVE_PCT_PC = 1)
```

@@

  normalizationType	= 'CQN',
  institution = 'MSSM'
)

# Code
CODE <- Folder(name = "ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN - MSSM", parentId = parentId)
annotations(CODE) = all.annotations
CODE <- synStore(CODE)

>>>>

knit2synapse::knitToFolderEntity(file = "./CMC_ACC_DLPFC_STAR_ENSEMBL_v75_CQN_PENN.Rmd",
                                 parentId = "syn7501880",
                                 entityName = 'ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN - PENN')
```

@@

METADATA = rbindlist(list(METADATA_ACC, METADATA_DLPFC), use.names = T, fill = T) %>%
  droplevels() %>%
  list(.,METADATA_QC) %>%
  join_all %>%
  dplyr::mutate(LibraryBatch = as.factor(LibraryBatch)) %>%
  left_join(ANCESTRY) %>%
  dplyr::filter(Institution == 'Penn') %>%
  unique

@@

### Covariates clustering
Determine relationship between covariates. 
```{r covariates.clustering}
FactorCovariates <- c("Individual_ID", "Institution", "Gender", "LibraryBatch", "Dx.Tissue", "RibozeroBatch", "FlowcellBatch")
ContCovariates <- c("Age_of_Death", "PMI", "RIN", "MappedReads", "IntragenicRate", "IntronicRate", "IntergenicRate",
                    "GenesDetected", "TranscriptsDetected", "ExpProfEfficiency", "rRNARate", "TotalReads", 
                    "PercentAligned", "EV.1", "EV.2", "EV.3", "EV.4", "EV.5")

@@

### Significant Covariates
Correlation between pca of unadjusted mRNA expression and covariates is used to find significant covariates
```{r preAdjusted.covariates, cache=TRUE}
# Find correlation between PC's of gene expression with covariates
preAdjustedSigCovars = runPCAandPlotCorrelations(CQN.GENE_EXPRESSION$E, 
                                                 COVARIATES[,setdiff(colnames(COVARIATES), c('Institution'))],
                                                 'NULL design(voom-normalized)', 
                                                 isKeyPlot=TRUE, 
                                                 MIN_PVE_PCT_PC = 1)
```

@@

  normalizationType	= 'CQN',
  institution = 'PENN'
)

# Code
CODE <- Folder(name = "ACC and DLPFC - STAR - FEATURE COUNTS - ENSEMBL v75 - CQN - PENN", parentId = parentId)
annotations(CODE) = all.annotations
CODE <- synStore(CODE)
